\section{Solution Methods}

\subsection{Data Set}

We plan to use SemCor Corpus~\cite{semcor} as our data set. SemCor Corpus is a
corpus where each word is tagged with a sense provided by WordNet~\cite{wordnet}.

\subsection{Feature extraction}

Let W be the set of English words that we want to do sense disambiguation. 

For each $w \in W$, we need to extract a training set $X_w$ from the SemCor
Corpus as follow: 
\begin{enumerate}
  \item Draw a set of sentences $S_w$ from SemCor Corpus, where each sentense
$s \in S_w$ contains the word w. 
  \item Convert each sentence $s \in S_w$ to a feature vector x, and the sense
    label y. The set of all (x,y) pairs is our training set $X_w$.
\end{enumerate}

\textbf{Feature extraction}. So far we have found two ways to convert a
sensetence to a feature vector that represents the sentence context for word
sense disambiguation task:
\begin{enumerate}
  \item Colocation~\cite{colocation}. The preceding and succeeding words.
  \item Bag-of-words~\cite{bagofwords}. Ignore positional information. Assume
    that there is a fixed set of vocabulary we care about, count the appearance
    of those words as a bit vector.
\end{enumerate}

\subsection{Algorithms}

For this multi-class classification problem, we consider the following models,
using one-vs-all method to extend them to solve multi-class problem:
\begin{enumerate}
  \item Naive Bayes.
  \item Logistic Regression.
  \item Support Vector Machine.
  \item Neural Networks.
\end{enumerate}

\subsection{Evaluation Method}

For each target word, we partition the data into training set and test set. And
evaluate classifiers on the training set using 0-1 loss.
